Time slice analyses

### 2018-02-06 analyses/02-time-slice-analyses.Rmd
Small comment about time the script takes to run
Change dispRity version to release version
Hide warnings in .Rmd

This code runs the analyses in the paper. Below we lay out the process in detail for one dataset, and then provide the code for the other datasets below this. Note that much of this uses functions in the `simulations_fun.R` file.

@@

## The latest version of dispRity
## install_github("TGuillerme/dispRity", ref = "master")
library(dispRity)

@@

```{r}
slug <- "Brusatte2014"

@@

```{r}
slug <- "Bapst2016"

@@

Wright 2017
-----------
```{r}
## Choose a slug
slug <- "Wright2017"

>>>>

This code runs the analyses in the paper. Below we lay out the process in detail for one dataset, and then provide the code for the other datasets below this. Note that much of this uses functions in the `simulations_fun.R` file. It also is also quite slow on some machines, but all outputs are available in the repo.

@@

## The latest version of dispRity
## install_github("TGuillerme/dispRity@v0.5")
library(dispRity)

@@

```{r, warning = FALSE}
slug <- "Brusatte2014"

@@

```{r, warning = FALSE}
slug <- "Bapst2016"

@@

Wright 2017
-----------
```{r, warning = FALSE}
## Choose a slug
slug <- "Wright2017"
